The fraction of polar aligned circumbinary disks

### 2025-04-04 src/tex/ms.tex
L35-38

Observed circumbinary planets -- those orbiting two stars -- have mostly been found to orbit in the same plane as their hosts \citep{doyle2011,orosz2012,welsh2012}. While this preference is the result of target selection effects (\citealt{martin2014}, see also \citealt{martin2015}, \citealt{martin2017a}), it is also representative of the fact that, for the disk progenitors of these planets \citep[from which the planets inherit orbital parameters, see][]{childs2021}, a coplanar alignment is one of two possible stable orientations \citep{bate2000,lubow2000}. The other configuration -- a polar disk -- is characterized by being inclined $90^\circ$ relative to the binary orbital plane \citep{aly2015,martin2017}. \RR{O}nly a handful of confirmed polar disks have ever been discovered. These include a polar debris disk in the 99 Her system (\citealt{kennedy2012}, which likely evolved from a polar gas disk, see \citealt{smallwood2020}) and polar gas disks in the HD 98800 \citep{kennedy2019} and V773 Tau \citep{kenworthy2022} systems. \RR{Evidence for one polar planet has been found via indirect means \citep[AC Her, ][]{hillen2015,anugu2023,martin2023}}

>>>>

Observed circumbinary planets -- those orbiting two stars -- have mostly been found to orbit in the same plane as their hosts \citep{doyle2011,orosz2012,welsh2012}. While this preference is the result of target selection effects (\citealt{martin2014}, see also \citealt{martin2015}, \citealt{martin2017a}), it is also representative of the fact that, for the disk progenitors of these planets \citep[from which the planets inherit orbital parameters, see][]{childs2021}, a coplanar alignment is one of two possible stable orientations \citep{bate2000,lubow2000}. The other configuration -- a polar disk -- is characterized by being inclined $90^\circ$ relative to the binary orbital plane \citep{aly2015,martin2017}. \RR{O}nly a handful of confirmed polar disks have ever been discovered. These include a polar debris disk in the 99 Her system (\citealt{kennedy2012}, which likely evolved from a polar gas disk, see \citealt{smallwood2020}) and polar gas disks in the HD 98800 \citep{kennedy2019} and V773 Tau \citep{kenworthy2022} systems. \RR{The only evidence for a polar planet in a circumbinary system comes from AC Her, a post-AGB system that hosts an unusually-truncated circumbinary disk, with a planet located interior to the disk's inner edge being the most likely cause \citep{hillen2015,anugu2023,martin2023}.}

### 2025-04-04 src/tex/review.tex
L35-38

>>>>

    \begin{response}
        {
            L35-38: The evidence pointed out by the authors for AC Her is extremely indirect and also around an evolved binary star with a CBD, for which the disc formation pathway and subsequent evolution remains very unclear. At the moment, this "evidence" is loosely supported by data as the planet was not confirmed/observed but simply proposed as the "most likely scenario" (Martin et al., 2023) based on disc truncation arguments alone. Therefore, I would strongly suggest to rephrase this part to avoid conveying the wrong idea to non-specialists.
        }
        We have changed the order of the text and changed the language so that this portion is clearer.
    \end{response}
